An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-28 draft.tex
Update draft.tex

The EvoSwarm application uses configuration files to run noiseless BOBB testbed
experiments. As a first step, the docker application must be deployed, using a
{\tt docker-compose.yml} file, where the number of worker containers is
specified. Then a JSON file containing the configuration parameters of the
experiment has to be provided. Table \ref{tab:params} shows an example of these
parameters. The {\em GA-PSO Ratio} parameter indicates the proportion of
populations that will use the GA algorithm for the search. With a value of
$0.50$ there will be about the same proportion of GA and PSO populations. If we
specify a value of $0$ this will give us a PSO only algorithm, and finally, a
value of $1$ means that all populations will run the GA algorithm. Next, we
specify a list indicating which of the 24 benchmark functions will be tested.
In the example, the experiment will use the first five functions. The
{\em Instances} parameter, indicates how many instances of each function will be
executed, this parameter has 15 as the default value. This value is used
because is the standard for the BBOB benchmark \cite{hansen2016coco}. Then, in
the {\em Dimensions} parameter we define a list of the dimensions that will be
tested, we must select additional parameters for each dimension. According to
the maximum number of Function Evaluations (FEs) we mentioned earlier, we
define for each dimension: the number of populations that will be generated in
the setup, and for each population, the number of generations, and population
size. Finally, the {\em Iterations} parameter indicates how many complete loops
will be performed. All these parameters give us the maximum number of FEs that
will be performed. For instance, for $D = 2$, the maximum number of FEs is
$200,000$ which is the same as $40*50*10*10$.

>>>>

The EvoSwarm application uses configuration files to run noiseless BOBB testbed
experiments.  As a first step, we must deploy the docker application using a
{\tt docker-compose.yml} file, where the number of worker containers is
specified. Then a JSON file containing the configuration parameters of the
experiment has to be provided.  Table \ref{tab:params} shows an example of these
parameters. The \em{GA-PSO Ratio} parameter indicates the proportion of
populations that will use the GA algorithm.  In the example, with a value of
$0.50$ there will be about the same proportion of GA and PSO populations. If we
specify a value of $0$, this will give us an algorithm with only PSO
populations, and finally, a value of  $1$ means that all populations will run
the GA algorithm. Next, we specify a list indicating which of the 24 benchmark
functions will be tested. In the example, the experiment will use the first five
functions.  The \em{Instances} parameter indicates how many instances of each
function will be tested. \em{Instances}  has a defualt value of 15. We used this
value because it is the standard for the BBOB benchmark \cite{hansen2016coco}.
In the \em{Dimensions} parameter, we define a list of the dimensions that will
be tested, and we must select additional parameters for each dimension.
According to the maximum number of  Function Evaluations (FEs) we mentioned
earlier, we define for each dimension: the number of populations that will be
generated in the setup, and for each population,  the number of generations, and
population size. Finally, the \em{Iterations} parameter indicates how many
complete loops will be performed. All these parameters give us the maximum
number of FEs that will be performed. For instance, for $D = 2$, the maximum
number of FEs is $200,000$, which is the same as $40*50*10*10$.
